MADA Project Manuscript

### 2021-11-12 products/manuscript/Manuscript.Rmd
MADA project part 4-added abstract

# Summary/Abstract
_Write a summary of your project._

>>>>

# Abstract
COVID-19 has been the talk of the world for the past two years, and it is still prevalent. The affects of COVID-19 not only affected individual people, but it also affected businesses, health protocols, and the economy of governments. It has affected all countries not only specific to a type of country which is the scary part. It is truly indeed a pandemic.

I am interested in looking at the difference between the proportion of those who recovered to those who have died for each country in the world. I am also looking at how the proportion of people vaccinated in each country is affected by multiple factors. The predictors I will be considering are: percent of cases within a population, continent the country is on, number of tests per person, gdp per capita, proportion of those who died, government type, and health care funds.

By looking at some simple linear regressions and other exploratory analysis, I determined due to how high the recovery rate is within each country overall and no association based on R-squared values, the difference in proportions did not change based on multiple factors.

While looking at vaccination proportions, I decided to do some analyses using training/test data sets and applying them to find the RMSE of the full model and a null model. When finding the RMSE, I found that the full model does a better job in fitting the data compared to the null model. This is a good sign to share that some combination of predictors have an association to the proportion of vaccinated people for each country.

The next analysis was creating a machine learning modeling technique called the LASSO model. This type of modeling will create multiple models from a five-fold cross-validation and a tuning grid which will try to find the best performing model. From the LASSO we find that model 25 give the best model.

**Need to find a way to extract this model**
